---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# likert2dummy


The goal of likert2dummy is to turn 5-pt Likert-scale or Likert-type scale items into dummy variables. This function converts 5-pt Likert scales to dummy variables using the rule that a 4 or 5 on a Likert scale will = 1 on the dummy scale, and a 3, 2, or 1 on Likert scale will = 0 on a dummy scale.


## Installation

You can install the released version of likert2dummy from Github using:

``` r
# install.packages("devtools")
devtools::install_github("asanto0803/STAT545AssignmentB2/")
```
## Example

This is a basic examples which shows you how to solve a common problem:

```{r example}
library(likert2dummy)

# Example 1
var1 <- c(1,3,5,4,2,3,1)
var2 <- c(2,4,5,NA,2,1,1)
df <- data.frame(var1, var2)
likert2dummy(df, var1)
likert2dummy(df, var2)
```
